---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shilohkira

<!-- badges: start -->
<!-- badges: end -->

shilohkira is a package that makes data fun and easy! The goal of shilohkira is to help you more efficiently work with any data of your choice, as well as introduce you to a mortality dataset recording the death rates across country and other demographics including age and gender. 

With this package, you would be able to interactively work with R console prompts to filter through and change different values across a column, as well as to fix non-numeric values to any user inputs and decisions of your choice. While it's all up to your discretion, our package helps you streamline the process.

In addition, our package helps you visualize your data. We help you make a scatterplot graphing changes over time for different treatment groups, and another chart plotting changes in weight over time for each sample you have in the dataset. We also generate a summary statistics table one for your data so you can get a sense of how your samples change over time in numerical format as well. 

## Installation

You can install the development version of shilohkira like so:

If you were running the folder on your computer locally, open up the shilohkira folder and run the code `devtools::install()' since this function essentially replaces the `install.packages("shilohkira")' function. Then you can run `library(shilohkira)' as usual and you would be able to use all the different functions in our package!

We also pushed our package onto GitHub, so you would also be able to install the pacakge from GitHub by running `devtools::install_github("shilohliu0810/shilohkira2")'.

##Data

We are also introducing you to the mortality dataset ["https://ghdx.healthdata.org/record/ihme-data/gbd-2010-mortality-results-1970-2010"] in our package. This dataset contains data of mortality by age and sex across countries over time from 1970-2010, for 187 countries in the world. This is an important dataset to explore if you want to see how mortality and death rates, whether as a result as crime, health, or other factors, vary across countries considering the regions that they are located and the socioeconomic characteristics comparisons. 

It is especially useful to apply our functions to this dataset for cleaning purposes, and making columns numeric or renaming deviant values are also functions that are generalizable across all types of data cleaning. As for plotting purposes, since the mortality dataset is consisted of two different genders, as with the idea of having a placebo and treatment group for our sample mouse dataset, we are also able to be useful in helping you plot differences across these two genders in terms of mortality rate or death rate trends over time. The time series component of this dataset also makes it applicable to our package because we are able to help you plot different countries all on the same graph for displaying changes over time. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(shilohkira)
```

```{r example}
## basic example code
install.packages("readxl")
library(readxl)
library(tidyverse)
setwd("/Users/shilohliu/Dropbox/shilohkira2")
sheet_names <- excel_sheets("data-raw/mousedata.xlsx")
all_sheets <- lapply(sheet_names, function(sheet) {
  read_excel("/Users/shilohliu/Dropbox/shilohkira2/data-raw/mousedata.xlsx", sheet = sheet)
})
names(all_sheets) <- sheet_names
Birth <- all_sheets[[1]]    
Bodyweight <- all_sheets[[2]] 
Outcome <- all_sheets[[3]]  

newBirth <- check_and_rename_levels(Birth, "Treatment")
Bodyweight2 <- make_column_numeric_interactive(Bodyweight, "Body Weight 2")
Bodyweight3 <- make_column_numeric_interactive(Bodyweight, "Body Weight 3")
Bodyweight1 <- make_column_numeric_interactive(Bodyweight, "Body Weight 1")
weight_trends(
  dataset = newBirth,
  bodyweight_data = Bodyweight2,
  id_col = "ID",
  grouping_col = "Treatment",
  weight_cols = c("Body Weight 1", "Body Weight 2", "Body Weight 3"),
  time_points = c("Week 1", "Week 2", "Week 3"),
  merge_needed = TRUE
)
```

```{r}
Bodyweight2 <- make_column_numeric_interactive(Bodyweight, "Body Weight 2")
Bodyweight2 <- make_column_numeric_interactive(Bodyweight, "Body Weight 3")
Bodyweight2 <- make_column_numeric_interactive(Bodyweight, "Body Weight 1")

library(plotly)
wrongnum(
  bodyweight_data = Bodyweight2,
  id_col = "ID",
  weight_cols = c("Body Weight 1", "Body Weight 2", "Body Weight 3"),
  time_points = c("Week 1", "Week 2", "Week 3")
)
```
